Privacy Calculus Experiment

### 2023-04-12 analyses.Rmd
- Language updates

    #general
    version = factor(
      VE01_01, 
      labels = c(
        "Control", 
        "Like", 
        "Like & Dislike"
        )
      ),
    version_lkdslk = factor(
      version, 
      levels = c(
        "Like & Dislike", 
        "Like", 
        "Control"
        )
      ),
    version_no = recode(
      version, 
      "Control" = 1, 
      "Like" = 2, 
      "Like & Dislike" = 3
      ),
    male = replace_na(
      male, 
      "[3]") %>% 
      dplyr::recode(
        "männlich [1]" = 1, 
        "weiblich [2]" = 0
        ),
    age_grp = cut(
      age, 
      breaks = c(0, 29, 39, 49, 59, 100), 
      labels = c("<30", "30-39", "40-49", "50-59", ">59")
      ),

    # contrasts
    like = recode(
      version, 
      "Control" = 0, 
      "Like" = 1, 
      "Like & Dislike" = 0
      ),
    likedislike = recode(
      version, 
      "Control" = 0, 
      "Like" = 0, 
      "Like & Dislike" = 1
      ),
    control = recode(
      version, 
      "Control" = 1, 
      "Like" = 0, 
      "Like & Dislike" = 0
      ),

@@

words_m_lkdslk <- 
  fig_wrds_ctrl$data %>% 
  filter(effect1__ == "Like & Dislike") %>% 
  select(estimate__)

@@

```{r}
tab_slopes <- 
  rbind(
    slopes_wrds_pricon,
    slopes_wrds_grats,
    slopes_wrds_pridel,
    slopes_wrds_trust,
    slopes_wrds_selfeff,
    slopes_wrds_ctrl,
    slopes_wrds_lkdslk,
    slopes_pricon_ctrl,
    slopes_pricon_lkdslk,
    slopes_grats_ctrl,
    slopes_grats_lkdslk,
    slopes_pridel_ctrl,
    slopes_pridel_lkdslk,
    slopes_trust_ctrl,
    slopes_trust_lkdslk,
    slopes_selfeff_ctrl,
    slopes_selfeff_lkdslk
    ) %>% 
  as.data.frame() %>% 
  mutate(
    term = ifelse(
      .$contrast == "Like - Control", 
      "Like - Control",
      ifelse(
        .$contrast == "Like & Dislike - Control", 
        "Like & Dislike - Control",
        ifelse(
          .$contrast == "Like - Like & Dislike", 
          "Like - Like & Dislike", 
          .$term
          )
        )
      ),
    Predictor = recode(
      term, 
      "Like - Control" = "Like vs.control",
      "Like & Dislike - Control" = "Like & dislike vs.control",
      "Like - Like & Dislike" = "Like vs.like & dislike",
      "pri_con_fs" = "Privacy concerns",
      "pri_del_fs" = "Privacy deliberation",
      "grats_gen_fs" = "Expected gratifications",
      "trust_gen_fs" = "Trust",
      "self_eff_fs" = "Self-efficacy"
    ),
    Outcome = recode(
      Outcome,
      "pri_con_fs" = "Privacy concerns",
      "pri_del_fs" = "Privacy deliberation",
      "grats_gen_fs" = "Expected gratifications",
      "trust_gen_fs" = "Trust",
      "self_eff_fs" = "Self-efficacy"
    )
  ) %>% 
  filter(
    Predictor %in% c(
      "Like vs.control",
      "Like & dislike vs.control",
      "Like vs.like & dislike",
      "Privacy concerns",
      "Privacy deliberation",
      "Expected gratifications",
      "Trust",
      "Self-efficacy")
  ) %>% 
  mutate(
    Predictor = factor(Predictor, levels = c(
      "Self-efficacy",
      "Trust",
      "Privacy deliberation",
      "Expected gratifications",
      "Privacy concerns",
      "Like vs.like & dislike",
      "Like & dislike vs.control",
      "Like vs.control"
      )
    ),
    Estimate = 
      ifelse(
        Outcome == "words",
        round(estimate),
        estimate
      ),
    LL = 
      ifelse(
        Outcome == "words",
        round(conf.low),
        conf.low
      ),
    UL = 
      ifelse(
        Outcome == "words",
        round(conf.high),
        conf.high
      ),
  ) %>% 
  select(
    Outcome,
    Predictor, 
    Estimate,
    LL, 
    UL
    )

>>>>

    #general
    version = factor(
      VE01_01, 
      labels = c(
        "Control", 
        "Like", 
        "Like & dislike"
        )
      ),
    version_lkdslk = factor(
      version, 
      levels = c(
        "Like & dislike", 
        "Like", 
        "Control"
        )
      ),
    version_no = recode(
      version, 
      "Control" = 1, 
      "Like" = 2, 
      "Like & dislike" = 3
      ),
    male = replace_na(
      male, 
      "[3]") %>% 
      dplyr::recode(
        "männlich [1]" = 1, 
        "weiblich [2]" = 0
        ),
    age_grp = cut(
      age, 
      breaks = c(0, 29, 39, 49, 59, 100), 
      labels = c("<30", "30-39", "40-49", "50-59", ">59")
      ),

    # contrasts
    like = recode(
      version, 
      "Control" = 0, 
      "Like" = 1, 
      "Like & dislike" = 0
      ),
    likedislike = recode(
      version, 
      "Control" = 0, 
      "Like" = 0, 
      "Like & dislike" = 1
      ),
    control = recode(
      version, 
      "Control" = 1, 
      "Like" = 0, 
      "Like & dislike" = 0
      ),

@@

words_m_lkdslk <- 
  fig_wrds_ctrl$data %>% 
  filter(effect1__ == "Like & dislike") %>% 
  select(estimate__)

@@

```{r}
tab_slopes <- 
  rbind(
    slopes_wrds_pricon,
    slopes_wrds_grats,
    slopes_wrds_pridel,
    slopes_wrds_trust,
    slopes_wrds_selfeff,
    slopes_wrds_ctrl,
    slopes_wrds_lkdslk,
    slopes_pricon_ctrl,
    slopes_pricon_lkdslk,
    slopes_grats_ctrl,
    slopes_grats_lkdslk,
    slopes_pridel_ctrl,
    slopes_pridel_lkdslk,
    slopes_trust_ctrl,
    slopes_trust_lkdslk,
    slopes_selfeff_ctrl,
    slopes_selfeff_lkdslk
    ) %>% 
  as.data.frame() %>% 
  mutate(
    term = ifelse(
      .$contrast == "Like - Control", 
      "Like - Control",
      ifelse(
        .$contrast == "Like & dislike - Control", 
        "Like & dislike - Control",
        ifelse(
          .$contrast == "Like - Like & dislike", 
          "Like - Like & dislike", 
          .$term
          )
        )
      ),
    Predictor = recode(
      term, 
      "Like - Control" = "Like vs. control",
      "Like & dislike - Control" = "Like & dislike vs. control",
      "Like - Like & dislike" = "Like vs. like & dislike",
      "pri_con_fs" = "Privacy concerns",
      "pri_del_fs" = "Privacy deliberation",
      "grats_gen_fs" = "Expected gratifications",
      "trust_gen_fs" = "Trust",
      "self_eff_fs" = "Self-efficacy"
    ),
    Outcome = recode(
      Outcome,
      "pri_con_fs" = "Privacy concerns",
      "pri_del_fs" = "Privacy deliberation",
      "grats_gen_fs" = "Expected gratifications",
      "trust_gen_fs" = "Trust",
      "self_eff_fs" = "Self-efficacy"
    )
  ) %>% 
  filter(
    Predictor %in% c(
      "Like vs. control",
      "Like & dislike vs. control",
      "Like vs. like & dislike",
      "Privacy concerns",
      "Privacy deliberation",
      "Expected gratifications",
      "Trust",
      "Self-efficacy")
  ) %>% 
  mutate(
    Predictor = factor(Predictor, levels = c(
      "Self-efficacy",
      "Trust",
      "Privacy deliberation",
      "Expected gratifications",
      "Privacy concerns",
      "Like vs. like & dislike",
      "Like & dislike vs. control",
      "Like vs. control"
      )
    ),
    Estimate = 
      ifelse(
        Outcome == "words",
        round(estimate),
        estimate
      ),
    LL = 
      ifelse(
        Outcome == "words",
        round(conf.low),
        conf.low
      ),
    UL = 
      ifelse(
        Outcome == "words",
        round(conf.high),
        conf.high
      ),
  ) %>% 
  select(
    Outcome,
    Predictor, 
    Estimate,
    LL, 
    UL
    )

### 2023-04-12 index.Rmd
- Language updates

On this website, you can find the companion material for the paper _Like or Dislike, Gratifications or Concerns? Analyzing Popularity Cues and Privacy Calculus in Online Communication_.

>>>>

On this website, you can find the companion material for the paper _Likes or Dislikes, Gratifications or Concerns? Analyzing the Effects of Popularity Cues on the Privacy Calculus in Online Communication_.
